---
title: "Untitled"
author: "Alex"
date: "5/30/2021"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

#Setup:
library(tidyr)
library(lattice)
library(readxl)
library(ggplot2)
library(data.table)
library(dplyr)
library(glue)
library(nlme)
library(reshape2)
library(aomisc)
library(drmdel)
library(drc)
library(stringr)
library(ModelMetrics)
library(broom)
library(CARRoT)
library(caret)
```

```{r echo = T, results = 'hide', error=FALSE, warning=FALSE, message=FALSE}
#Data Acquisition ---------
inputdata <- read_excel("./inputdata.xlsx") #, sheet = "raw_data")
regression.results <- read.csv("./regression.results.csv")
regression.results <- subset(regression.results[,2:9])

RawData <- inputdata[2]
is.data.frame(RawData)

RawData <- cbind(RawData, inputdata["COSMIC_ID"], inputdata["CELL_LINE_NAME"], inputdata["DRUG_ID"], inputdata["CELL_ID"], inputdata["MASTER_CELL_ID"], inputdata["SEEDING_DENSITY"], inputdata["ASSAY"], inputdata["DURATION"], inputdata["POSITION"], inputdata["TAG"], inputdata["CONC"], inputdata["INTENSITY"])

#Cleaning Up
CleanData <- RawData
CleanData[CleanData == "NA"] <- "0"

#Parsing Grouping Chunks -------------
ChunkStarts <- which(grepl("D1", CleanData$TAG))
print(ChunkStarts)

ChunkStarts <- ChunkStarts[0:2]
```

```{r}
#Table Prep and Graphing Start ---
biphasic.regressionresults <- as.data.frame(c())
gompertz.regressionresults <- as.data.frame(c())


for (w in ChunkStarts){
w <- as.numeric(w)
  tempterm <- w+9
  ProcessingSubset <- CleanData %>% slice(w:tempterm)

#Find Negative Controls
tempterm <- ProcessingSubset$CELL_LINE_NAME[2]
tempvector <- which(grepl(tempterm, CleanData$CELL_LINE_NAME))
tempdata <- CleanData %>% slice(min(tempvector):max(tempvector))
tempdata <- cbind(tempdata, tempvector)
tempdata <- tempdata %>% filter(tempdata$TAG == "NC-0")
NC0 <- mean(tempdata$INTENSITY)

#Normalization Calculations
tempdata <- ProcessingSubset["CONC"]
tempdata <- cbind(tempdata, ProcessingSubset["INTENSITY"])
tempdata[tempdata == "NA"] <- "0"
tempdata <- as.data.frame(tempdata)
tempvector <- as.vector(tempdata$INTENSITY)
ProcessingSubset$CONC <- as.numeric(ProcessingSubset$CONC)
ProcessingSubset["lnCONC"] <- log(ProcessingSubset["CONC"])
ProcessingSubset["RELATIVE_VIABILITY"] <- (tempvector - 30000)/(NC0 - 30000)
 
#Import Data - Change Name for different tables of Cell/Drug Combos error 
equation_test_data <- ProcessingSubset[1:10,3:4]
equation_test_data <- cbind(equation_test_data, ProcessingSubset[1:10,12:15])
equation_test_data[equation_test_data == "Inf"] <- 10
equation_test_data[equation_test_data == "-Inf"] <- -10

ActiveName <- paste(equation_test_data$CELL_LINE_NAME[1],equation_test_data$DRUG_ID[2], sep="_")
# Data Prep
x <- -1*equation_test_data$CONC
y <- equation_test_data$RELATIVE_VIABILITY

#Zeroing & Normalizing by subtraction of smallest
#tempterm <- min(x)
#x <- x-tempterm

if (sd(x) <= .1){
  tempvector <- c(ActiveName, "No Drug", 0, 0, 0, 0, NA, NA)
  biphasic.regressionresults <- rbind(biphasic.regressionresults, tempvector)
  next
  } 

if (sd(y) <= .1){
  tempvector <- c(ActiveName, "Not Effective", 0, 0, 0, 0, NA, Inf)
  biphasic.regressionresults <- rbind(biphasic.regressionresults, tempvector)
  next()
  } 

#Zeroing & Normalizing by subtraction of smallest term
#x <- x-min(x)
#tempterm <- as.numeric(which.max(y))
#y[tempterm:8] <- 1

testdata <- as.data.frame(x)
testdata <- cbind(testdata, y)
#testdata[] <- round(testdata[], digits = 3)
testdata[testdata == "Inf"] <- 10
testdata[testdata == "-Inf"] <- -10
testdata <- as.data.frame(testdata)

#Biphasic Model Regression Calculations ------------------------
#inputs
activefunction <- function(x) {a*x/(b+x)+(1-a)*x/(c+x)}
offset.activefunction <- function(x) {a*(x)/(b+(x))+(1-a)*(x)/(c+(x))}
biphasic.function <- offset.activefunction
  #function(x) {biphasic.results$a*(x-biphasic.results$d)/(biphasic.results$b+(x-biphasic.results$d))+(1-biphasic.results$a)*(x-biphasic.results$d)/(biphasic.results$c+(x-biphasic.results$d))}

# a and b coded to never equal 0
x <- testdata$x
y <- testdata$y
z <- c(0:2)  #iterations
s <- 3        #Number of subdivisions to do during regression
a <- c(-1,1)  #F1 term
b <- c(-1,1) #Kd1
c <- c(-1,1) #Kd2
d <- c(-1,10) #currently the offset for when Imax is reached

source(file = "dirtyregression.R", local = TRUE)

#outputs
biphasic.results <- results[order(results$RMSEscore), ] [1,]
a <- as.numeric(biphasic.results$a)
b <- as.numeric(biphasic.results$b)
c <- as.numeric(biphasic.results$c)
d <- as.numeric(biphasic.results$d)
RMSE <- as.numeric(biphasic.results$RMSEscore)

#Calculations
predict_y <- biphasic.function(x)

tempterm <- 0.5*(2*a*b - b - 2*a*c + c + sqrt(((2*a - 1)*b - 2*a*c + c)^2 + 4*b*c))
tempterm2 <- 0.5*(2*a*b - b - 2*a*c + c - sqrt(((2*a - 1)*b - 2*a*c + c)^2 + 4*b*c))

IC50 <- -1*(min((0-tempterm), (0-tempterm2)))

#Construct Results CSV
tempvector <- c(ActiveName, "Biphasic Model", a, b, c, d, RMSE, IC50)
biphasic.regressionresults <- rbind(biphasic.regressionresults, tempvector)
colnames(biphasic.regressionresults) <- c("ActiveName", "Biphasic Model", "a", "b", "c", "d", "RMSEscore", "IC50")

#Graph Label
temptext <- paste(ActiveName, "Dirty Biphasic Regression", sep = " ")
biphasic.graph.text <- paste("Biphasic: F1 = ", a, ", Kd1 = ", b, ", Kd2 = ", c, " Offset = ", d, ", RMSE ", RMSE, ", IC50 = ", IC50, sep = "")


#Graphing
x <- -1*equation_test_data$lnCONC
x <- x - min(x)
y <- equation_test_data$RELATIVE_VIABILITY
tempdata <- x
tempdata <- as.data.frame(cbind(tempdata, y))
tempdata <- as.data.frame(cbind(tempdata, predict_y))

tempterm <- max(max(x), IC50)
ggplot(data = tempdata, aes(x = tempdata, y = y)) +
        geom_point()+
        geom_line(data = tempdata, aes(x = x, y = predict_y))+
        geom_function(fun = biphasic.function)+ 
        #scale_x_log10(limits = c(-3, 12))+
        labs(title = temptext, x = "lnCONC", y = "Relative Viability") +
        annotate(geom = "text", x = max(x)/2 ,  y=1.5, label = str_wrap(biphasic.graph.text, 100))+
        ylim(0, 1.5)+
        xlim(-1, max(x)) +
  ggsave(plot = last_plot(), filename = paste(ActiveName, "_Dirty_Gompertz_Plot.png", sep = ""), width = 10, height = 10, device = NULL)

}
colnames(biphasic.regressionresults) <- c("ActiveName", "Model", "a (F1)", "b (Kd1)", "c (Kd2)", "d (Offset)", "RMSEscore", "IC50")
colnames(regression.results) <- c("ActiveName", "Model", "a (F1)", "b (Kd1)", "c (Kd2)", "d (Offset)", "RMSEscore", "IC50")
      
regression.results <- rbind(regression.results, biphasic.regressionresults)   

regression.results <- distinct(regression.results, ActiveName,IC50, .keep_all = TRUE)
Export(regression.results, "./regression.results.csv", format = "csv", keep.row.names = TRUE)
```
#Gompertz Model Regression Calculations -----------
      activefunction <- function(x) {c+(a-c)*exp(-exp(-b*(x-d)))}
      offset.activefunction <- function(x) {c+(a-c)*exp(-exp(-b*(x-d)))}
      gompertz.function <- function(x) {gompertz.results$c+(gompertz.results$a-gompertz.results$c)*exp(-exp(-gompertz.results$b*(x-gompertz.results$ d)))}
       
      # a and b coded to never equal 0
      x <- testdata$x
      y <- testdata$y
      z <- c()  #iterations
      s <- 5        #Number of subdivisions to do during regression
      a <- c(-1,1)  # gomp d
      b <- c(-1,1)  # gomp b
      c <- c(-1,1)  # gomp c
      d <- c(-1,1)  # gomp e
      
      source(file = "dirtyregression.R", local = TRUE)

    #outputs
      gompertz.results <- results[order(results$RMSEscore), ] [1,]
      a <- as.numeric(gompertz.results$a)
      b <- as.numeric(gompertz.results$b)
      c <- as.numeric(gompertz.results$c)
      d <- as.numeric(gompertz.results$d)
      RMSE <- as.numeric(gompertz.results$RMSEscore)
      
      #Calculate IC50
      IC50 <- (b*d - log(log(-1*(2*c - 2*a)/(1 - 2*c))))/b
      
      #Construct Results CSV
      tempvector <- c(ActiveName, "Gompertz Model", a, b, c, d, RMSEscore, IC50)
      gompertz.regressionresults <- rbind(gompertz.regressionresults, tempvector)
      colnames(gompertz.regressionresults) <- c("ActiveName", "Gompertz Model", "a", "b", "c", "d", "RMSEscore", "IC50") tempterm <- max(max(x), IC50)
      
      #Graph Function
      temptext <- paste(ActiveName, "Dirty Gompertz Regression", sep = " ")
      temptext2 <- paste("Gompertz: a = ", a, ", b = ", b, ", c = ", c, " d = ", d, ", RMSE ", RMSE, ", IC50 = ", IC50, sep = "")
      tempterm <- max(max(x), IC50)
    
      ggplot(data = testdata, aes(x = x, y = y)) +
        geom_point()+
        geom_function(fun = gompertz.function)+ 
        labs(title = temptext, x = "LnCONC", y = "Relative Viability") +
        annotate(geom = "text", x = (max(x)/2), y=1.3, label = str_wrap(temptext2, 100)) +
        geom_function(fun = biphasic.function, aes(col = 2))+
        annotate(geom = "text", x = (tempterm/2), y=1.5, label = str_wrap(biphasic.graph.text, 100), color = "blue")+
        ylim(0, 1.5)+
        xlim(-10, 10)+
        ggsave(plot = last_plot(), filename = paste(ActiveName, "_Dirty_Gompertz_Plot.png", sep = ""), width = 10, height = 10, device = NULL)

# End Gompertz ------------------------------------
}
colnames(biphasic.regressionresults) <- c("ActiveName", "Model", "a (F1)", "b (Kd1)", "c (Kd2)", "d (Offset)", "RMSEscore", "IC50")
colnames(gompertz.regressionresults) <- c("ActiveName", "Model", "a (F1)", "b (Kd1)", "c (Kd2)", "d (Offset)", "RMSEscore", "IC50")
colnames(regression.results) <- c("ActiveName", "Model", "a (F1)", "b (Kd1)", "c (Kd2)", "d (Offset)", "RMSEscore", "IC50")
      
regression.results <- rbind(regression.results, biphasic.regressionresults)   
regression.results <- rbind(regression.results, gompertz.regressionresults)  

regression.results <- distinct(regression.results, ActiveName,IC50, .keep_all = TRUE)
Export(regression.results, "./regression.results.csv", format = "csv", keep.row.names = TRUE)
```


