---
title: "Untitled"
author: "Alex"
date: "5/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE}
#Equation Regressions and Plotting

#Setup:
library(tidyr)
library(lattice)
library(reshape2)
library(readxl)
library(ggplot2)
library(data.table)
library(dplyr)
library(deSolve)
library(glue)
library(CARRoT)
library(caret)
library(nlme)
library(ggplot2)
library(broom)
#Repeat Libraries to reduce error
library(reshape2)
library(readxl)
library(ggplot2)
library(data.table)
library(dplyr)
library(deSolve)
library(glue)
library(CARRoT)
library(caret)
library(nlme)
library(ggplot2)
library(broom)

inputdata <- read.csv("equation.test.data.csv", nrows = 10)

#Import Data - Change Name for different tables of Cell/Drug Combos 
equation_test_data <- inputdata$CELL_LINE_NAME
equation_test_data <- cbind(equation_test_data, inputdata$DRUG_ID)
colnames(equation_test_data) <- c("CELL_LINE_NAME","DRUG_ID")
equation_test_data <- cbind(equation_test_data, inputdata[1:10,13:19])
equation_test_data[equation_test_data == "NA"] <- 0
equation_test_data[equation_test_data == "Inf"] <- 10
equation_test_data[equation_test_data == "-Inf"] <- -10

ActiveName <- paste(equation_test_data$CELL_LINE_NAME[1],equation_test_data$DRUG_ID[2], sep="_")

# Check Plot for Errors 
plot(-1*equation_test_data$lnCONC, equation_test_data$RELATIVE_VIABILITY, xlab = "LnCONC", ylab = "Relative Viability", main = paste(ActiveName, "BasePlot 1", sep = ""))
plot(-1*equation_test_data$CONC, equation_test_data$RELATIVE_VIABILITY, xlab = "CONC", ylab = "Relative Viability", main = paste(ActiveName, "BasePlot 2", sep = ""))

# Data Prep
x <- -1*equation_test_data$lnCONC
y <- equation_test_data$RELATIVE_VIABILITY

#Zeroing & Normalizing by subtraction of smallest term
tempterm <- min(x)
#x <- x-tempterm
if (min(y) <= 0) {
  tempterm <- min(y)
  y <- y-tempterm} else {y <- y}

testdata <- as.data.frame(x)
testdata <- cbind(testdata, y)
testdata[] <- round(testdata[], digits = 3)
testdata[testdata == "Inf"] <- 10
testdata[testdata == "-Inf"] <- -10
testdata <- as.data.frame(testdata)

# Determine Offset for real-values

offset <- max(equation_test_data$lnCONC)

#Set Generic Weighting; favor values closer to ".5"
generic_weighting <- .3 + (1-.3)*exp(-10*(testdata$y-.5)^2)
testdata$generic_weighting <- generic_weighting
```

```{r}
########################### Start of Linear Regression Modeling ###########################
  lm(formula = y ~ x , data = testdata, weights = testdata$weighting)

  summary <- lm(formula = y ~ x , data = testdata, weights = testdata$generic_weighting)
  summary$coefficients#
  a <- as.numeric(paste(summary$coefficients[1]))
  b <- as.numeric(paste(summary$coefficients[2]))

#Produce Equation, Calculate IC50, and Observe Most Likely IC50
  GeneratedEquation <- paste("I =", a, "+", b, "D)", sep = "")
  CalculatedIC50 <- (-summary$coefficients[1]+.5)/(summary$coefficients[2])
  ConcentrationNearestRV50 <- testdata %>% slice(which.min(.4), which.max(.6))
  ConcentrationNearestRV50 <- ConcentrationNearestRV50[1,]
  ConcentrationNearestRV50 <- as.vector(ConcentrationNearestRV50)
  CNRV50DifferenceTo.50 <- abs(ConcentrationNearestRV50[2] - 0.5)

#RMSE Calculations
  PredictedData <- a + b * x
  PredictedData[PredictedData == "Inf"] <- 1
  LinearRMSE <- RMSE(PredictedData, testdata$y)

#Graph Function
  temptext <- paste(ActiveName, "Linear Regression", sep = " ")
  temptext2 <- paste("a = ", a, ", b = ", b, sep = "")
  ggplot(data = testdata, aes(x = x, y = y)) +
    geom_point()+
    geom_function(fun = function(x) summary$coefficients[1] + summary$coefficients[2]*x) +
    labs(title = temptext, subtitle = temptext2, x = "LnCONC", y = "Relative Viability") +
    ylim(0, 1.5)+
    ggsave(plot = last_plot(), filename = "LinearEquationReportPlot.png", width = 4, height = 4, device = NULL)

#Write Report Data 
LinearEquationReport <- c(paste(GeneratedEquation), CalculatedIC50, LinearRMSE, as.vector(ConcentrationNearestRV50[1]), as.vector(ConcentrationNearestRV50[2]),CNRV50DifferenceTo.50)
LinearEquationReport <- as.data.frame(LinearEquationReport)
LinearEquationReport <- transpose(LinearEquationReport)
tempvector <- c("LN Equation", "CalculatedIC50", "LinearRMSE", "Concentration Nearest to RV50","RV Nearest to RV50","Difference between Nearest Value and .5")
as.data.frame(tempvector)
LinearEquationReport <- cbind(LinearEquationReport, tempvector)
```

```{r}
########################### Start of Simple Hills Regression Modeling ###########################
library(ModelMetrics)
library(aomisc)
library(drmdel)
library(drc)
library(nlme)
```
#Update Weighting to not favor multiple values of 0
simple_weighting <- c()
for (i in y) {
  print(i)
  if (i >= 0.1) {I = F 1 × [D]/([D] + K d1 ) + F 2 ×simple_testdata <- testdata
for (i in testdata$y){
  if (i <= .08){  
    if (i != 0){
      simple_testdata <- subset(simple_testdata, simple_testdata$y != i)
    } else (i <- i) 
  } else (i <- i)
}
simple_testdata$x <- simple_testdata$x-min(testdata$x)
x <- simple_testdata$x
x <- x - min(x)
y <- simple_testdata$y

# Using a Simple Regression based off the MM-2 Variable model
Simplemodel <- drm(y ~ x, fct = MM.2(fixed = c(1, NA))) #, weights = testdata$simple_weighting)
Simplemodel$coefficients
a <- 1 #Change to >> "as.numeric(paste(Simplemodel$coefficients[1]))" and update "b" if not slope of 1
b <- as.numeric(paste(Simplemodel$coefficients[1]))

# Produce Equation, Calculate IC50, and Observe Most Likely IC50
GeneratedEquation <- paste("I =", a, "D/(", b, "+ D)", sep = "")
CalculatedIC50 <- (.5*b/a)/(1-.5/a)+offset

tempterm <- which(abs(testdata$y - .5) == min(abs(testdata$y -.5)))
tempterm <- as.numeric(tempterm)
ConcentrationNearestRV50 <- testdata[tempterm,1] + offset
CNRV50DifferenceTo.50 <- testdata[tempterm,2]
CNRV50DifferenceTo.50 <- abs(CNRV50DifferenceTo.50 - 0.5)

#I = D/(D + IC50) >I = F 1 × [D]/([D] + K d1 ) + F 2 × [D]/([D] + K d2 )> I = ***)
#RMSE Calculations
tempvector <- b + x
PredictedData <- a * x / tempvector
PredictedData[PredictedData == "Inf"] <- 1
SimpleRMSE <- RMSE(PredictedData, testdata$y)

#Graph Function
temptext <- paste(ActiveName, "Simple Hills Regression", sep = " ")
temptext2 <- paste("a = ", a, ", b = ", b, " Offset = ", offset, sep = "")
ggplot(data = simple_testdata, aes(x = x, y = y)) +
  geom_point()+
  geom_function(fun = funI = F 1 × [D]/([D] + K d1 ) + F 2 × [D]/([D] + K d2 )ction(x) (x-min(x))/(b+(x-min(x)))) +
  labs(title = temptext, subtitle = temptext2, x = "LnCONC", y = "Relative Viability") +
  ylim(0, 1.5) +
  ggsave(plot = last_plot(), filename = "SimpleEquationReportPlot.png", width = 4, height = 4, device = NULL)

#Write Report Data
SimpleEquationReport <- c(paste(GeneratedEquation), CalculatedIC50, SimpleRMSE, ConcentrationNearestRV50[1], ConcentrationNearestRV50[2], CNRV50DifferenceTo.50)
tempvector <- c("Simple Equation", "CalculatedIC50", "SimpleRMSE", "Concentration Nearest to RV50","RV Nearest to RV50","Difference between Nearest Value and .5")
as.data.frame(tempvector)
SimpleEquationReport <- cbind(SimpleEquationReport, tempvector)
SimpleEquationReport

``` [D]/([D] + K d2 )
  tempterm <-.3 + (1-.3)*exp(-exp(-10*(i-.3)))
  tempterm1 <- tempterm} else {tempterm1 <- .001}
 simple_weighting <- append(simple_weighting, tempterm1)
paste(simple_weighting)
 }
testdata$simple_weighting <- simple_weighting
```{r}
simple_testdata <- testdata
for (i in testdata$y){
  if (i <= .08){  
    if (i != 0){
      simple_testdata <- subset(simple_testdata, simple_testdata$y != i)
    } else (i <- i) 
  } else (i <- i)
}
simple_testdata$x <- simple_testdata$x-min(testdata$x)
x <- simple_testdata$x
x <- x - min(x)
y <- simple_testdata$y

# Using a Simple Regression based off the MM-2 Variable model
Simplemodel <- drm(y ~ x, fct = MM.2(fixed = c(1, NA))) #, weights = testdata$simple_weighting)
Simplemodel$coefficients
a <- 1 #Change to >> "as.numeric(paste(Simplemodel$coefficients[1]))" and update "b" if not slope of 1
b <- as.numeric(paste(Simplemodel$coefficients[1]))

# Produce Equation, Calculate IC50, and Observe Most Likely IC50
GeneratedEquation <- paste("I =", a, "D/(", b, "+ D)", sep = "")
CalculatedIC50 <- (.5*b/a)/(1-.5/a)+offset

tempterm <- which(abs(testdata$y - .5) == min(abs(testdata$y -.5)))
tempterm <- as.numeric(tempterm)
ConcentrationNearestRV50 <- testdata[tempterm,1] + offset
CNRV50DifferenceTo.50 <- testdata[tempterm,2]
CNRV50DifferenceTo.50 <- abs(CNRV50DifferenceTo.50 - 0.5)

#I = D/(D + IC50) >I = F 1 × [D]/([D] + K d1 ) + F 2 × [D]/([D] + K d2 )> I = ***)
#RMSE Calculations
tempvector <- b + x
PredictedData <- a * x / tempvector
PredictedData[PredictedData == "Inf"] <- 1
SimpleRMSE <- RMSE(PredictedData, testdata$y)

#Graph Function
temptext <- paste(ActiveName, "Simple Hills Regression", sep = " ")
temptext2 <- paste("a = ", a, ", b = ", b, " Offset = ", offset, sep = "")
ggplot(data = simple_testdata, aes(x = x, y = y)) +
  geom_point()+
  geom_function(fun = funI = F 1 × [D]/([D] + K d1 ) + F 2 × [D]/([D] + K d2 )ction(x) (x-min(x))/(b+(x-min(x)))) +
  labs(title = temptext, subtitle = temptext2, x = "LnCONC", y = "Relative Viability") +
  ylim(0, 1.5) +
  ggsave(plot = last_plot(), filename = "SimpleEquationReportPlot.png", width = 4, height = 4, device = NULL)

#Write Report Data
SimpleEquationReport <- c(paste(GeneratedEquation), CalculatedIC50, SimpleRMSE, ConcentrationNearestRV50[1], ConcentrationNearestRV50[2], CNRV50DifferenceTo.50)
tempvector <- c("Simple Equation", "CalculatedIC50", "SimpleRMSE", "Concentration Nearest to RV50","RV Nearest to RV50","Difference between Nearest Value and .5")
as.data.frame(tempvector)
SimpleEquationReport <- cbind(SimpleEquationReport, tempvector)
SimpleEquationReport

```

```{r}
########################### Start of Gompertz Regression Modeling ###########################

library(ModelMetrics)
library(aomisc)
library(drmdel)
library(drc)
library(nlme)

#Change Weightings to favor values of .5 to 1
testdata <- testdata[,1:2]
weighting_gompertz <- .3 + (1-.3)*exp(-exp(-10*(testdata$y-.3)))
weighting_gompertz <- as.data.frame(weighting_gompertz)
testdata <- cbind(testdata, weighting_gompertz)


testdata$y[10] <- 1
testdata$x[10] <- 10
y <- testdata$y
x <- testdata$x

#Y = d(1-exp(-exp(b(X-e))))
# Using a Simple Regression based off the MM-2 Variable model
Gompertzmodel <- drm(y ~ x, fct = G.3(fixed = c(NA, NA, NA), names = c("b", "d", "f")), weights = testdata$weighting_gompertz)
summary <- Gompertzmodel$coefficients
b <- as.numeric(summary[2])
d <- as.numeric(summary[1])
f <- as.numeric(summary[3])

#Graph Function
temptext <- paste(ActiveName, "Gomp Regression", sep = " ")
temptext2 <- paste("d = ", d, ", b = ", b, " e = ", f, sep = "")

ggplot(data = testdata, aes(x = x, y = y, group = 1)) +
  geom_point()+
  geom_function(fun = function(x) {d*exp(-exp(-b*(x - f)))}) + 
  labs(title = temptext, subtitle = temptext2, x = "LnCONC", y = "Relative Viability") +
  ylim(0, 1.5)+
  ggsave(plot = last_plot(), filename = "GompEquationReportPlot.png", width = 4, height = 4, device = NULL)

#Write Report Data
tempvector <- c("Gomp Equation", "CalculatedIC50", "Concentration Nearest to RV50","RV Nearest to RV50","Difference between Nearest Value and .5")
as.data.frame(tempvector)

GompEquationReport <- c(paste(GeneratedEquation), CalculatedIC50, summary[1], summary[2], summary[3], CNRV50DifferenceTo.50)
GompEquationReport <- cbind(GompEquationReport, tempvector)
GompEquationReport
```



