---
title: "randomizer testing"
author: "Alex"
date: "6/9/2021"
output: html_document
---

```{r setup, include=FALSE, error=FALSE, message=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
{ ####Setup: 
library(tidyr)
library(lattice)
library(reshape2)
library(readxl)
library(ggplot2)
library(data.table)
library(dplyr)
library(deSolve)
library(glue)
library(CARRoT)
library(caret)
library(nlme)
library(ggplot2)
library(broom) 
library(reshape2)
library(readxl)
library(ggplot2)
library(data.table)
library(dplyr)
library(deSolve)
library(glue)
library(CARRoT)
library(caret)
library(nlme)
library(ggplot2)
library(broom)
library(ModelMetrics)
#library(aomisc)
library(drmdel)
library(drc)
library(stringr) 
library(nlme)
library(openxlsx)
library(scales)
}
```


```{r}
inputdata <- read_xlsx("inputdata.xlsx", sheet = "AZD")

s <- 5
a <- c(0.2,0.84)
tempvector <- a
source(file = "range.randomizer_2.R", local = TRUE)

print(paste(range))
```

```{r}
randomizer = "range.randomizer_2.R"
x <- inputdata[,1]
y <- inputdata[,2]



ActiveName <- as.n(colnames(inputdata[,2]))



```
testdata <- as.data.frame(cbind(x,y))
{#Biphasic Model Regression Calculations ------------------------
#inputs
activefunction <- function(x) {1-a*x/(b+x)-(1-a)*x/(c+x)}
biphasic.function <- activefunction
z <- c(0:10)  #iterations
s <- 5       #Number of subdivisions to do during regression
a <- c(0,1)  #F1 term
b <- c(0,10) #Kd1
c <- c(0,10) #Kd2
d <- NA #currently the offset for when Imax is reached
}
source(file = "dirtyregression.R", local = TRUE)

{#outputs
biphasic.results <- results[order(results$RMSEscore), ] [1,]
a <- as.numeric(biphasic.results$a)
b <- as.numeric(biphasic.results$b)
c <- as.numeric(biphasic.results$c)
RMSE <- as.numeric(biphasic.results$RMSEscore)
}
{#Calculate IC50
tempterm <- 0.5*(2*a*b - b - 2*a*c + c + sqrt((-2*a*b + b + 2*a*c - c)^2 + 4*b*c))
tempterm2 <- 0.5*(2*a*b - b - 2*a*c + c - sqrt((-2*a*b + b + 2*a*c - c)^2 + 4*b*c))
IC50 <- max(tempterm, tempterm2)
}
{
#Construct Results CSV
tempvector <- c(ActiveName, "Biphasic Model", a, b, c, d, RMSEscore, IC50)
dirtyregressionresults <- rbind(dirtyregressionresults, tempvector)
colnames(dirtyregressionresults) <- c("ActiveName", "Model", "F#1", "Kd1", "Kd2", "NA", "RMSE", "IC50")

n <- max(length(x), length(y), length(tempvector))
length(x) <- n                      
length(y) <- n
length(tempvector) <- n

tempdata <- tempvector
tempdata <- cbind(tempdata, x)
tempdata <- cbind(tempdata, y)
tempterm <- paste("~/Desktop/plots/", ActiveName, "_Data.csv", sep = "")
write.csv(tempdata, file = tempterm)

#Graph Function
temptext <- paste(ActiveName, "Dirty Biphasic Regression", sep = " ")
biphasic.results <- paste("BiphasicModel: ", "F1=", round(a, digits = 8) , ", Kd1=", round(b, digits = 8), ", Kd2=", round(c, digits = 8), " Offset=", d, ", RMSE=", round(RMSE, digits = 8), ", IC50=", round(IC50, digits = 8), sep = "")
  
ggplot(data = inputdata, mapping = aes(x = x, y = y))+
  log_breaks(n = 5, base = 10)x_continuous(trans = "log10", limits = c(NA, 100))+
  ylim(0, 1.5) +
  ggsave(plot = last_plot(), filename = paste(ActiveName,"_Dirty_Biphasic_Plot.png", sep = ""), path = "~/Desktop/plots", width = 10, height = 10, device = NULL)
}
```

```{r}
randomizer = "range.randomizer_2.R"
x <- inputdata[,1]
y <- inputdata[,2]
ActiveName <- "AZD6244"
{#Biphasic Model Regression Calculations ------------------------
#inputs
activefunction <- function(x) {1-a*x/(b+x)-(1-a)*x/(c+x)}
biphasic.function <- activefunction
z <- c(0:10)  #iterations
s <- 5       #Number of subdivisions to do during regression
a <- c(0,1)  #F1 term
b <- c(0,10) #Kd1
c <- c(0,10) #Kd2
d <- NA #currently the offset for when Imax is reached
}

# Generate Starting Sequences from Ranges
all.runs <- transpose(as.data.frame(1:7))
colnames(all.runs) <- c("activename", "a","b","c","d","RMSEscore","Iterations")

# start of looping madness
for ( u in z) {
  u <- as.numeric(u)
  {  
  tempvector <- a
    source(file = paste(randomizer), local = TRUE)
  #a can not equal 0 nor 1
  a_list <- as.numeric(range[range > 0])
  a_list <- a_list[a_list < 1]
  
  tempvector <- b
    source(file = paste(randomizer), local = TRUE)
  #b can not equal 0
  b_list <- as.numeric(range[range > 0])

  tempvector <- c
    source(file = paste(randomizer), local = TRUE)
  c_list <- as.numeric(range) 
  c_list <- as.vector(c_list)

  }
  tempvector <- c()
  results <- transpose(as.data.frame(1:7))
  colnames (results) <- c("activename","a","b","c","d","RMSEscore","Iterations")
  for (a in a_list){"range.randomizer.R"
    for (b in b_list){
      for (c in c_list){
          predicted <- c() 
          predicted <- activefunction(x)
          predicted[is.na(predicted)] <- 0
          tempterm <- abs(RMSE(y, predicted))
          RMSEscore <- abs(tempterm)
          tempvector <- c(ActiveName, a, b, c, d, RMSEscore, u)
          results <- rbind(results, tempvector)
        } 
     }
  }
  {
  results <- subset(results, !is.na(results$RMSEscore))
  results <- subset(results, !is.infinite(results$RMSEscore))
  results <- distinct(results, .keep_all = FALSE)
  all.runs <- rbind(all.runs, results)
  
  results <- results[order(results$RMSEscore), ] [1:6,]
  a <- as.vector(results$a)
  b <- as.vector(results$b)
  c <- as.vector(results$c)
  #d <- as.vector(results$d)
  RMSE <- as.vector(results$RMSEscore)
  }
}

all.runs <- rbind(all.runs, results)
results <- results[order(results$RMSEscore), ] [1:6,]
```

